Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Directories
Iterate Data Model

\subsection{Directories \tbr}
\label{subsec:directories}

@@

\subsection{Data Model \tbr}
\label{subsec:data-model}

@@

Therefore, Spanner requires the application/user to partition databases into
one or more hierarchies of tables. Based on this hierarchical information, Spanner
builds the directories. A directory contains hierarchically ordered rows from
all tables of a hierarchy which belong to the same key of the topmost table of
the hierarchy. Figure~\ref{subfig:interleaved-tables} shows an examples of this
concept. In this example, the \texttt{Users} table is the topmost table of the
hierarchy and the \texttt{Albums} table is one level below. As we can see, all
rows of \texttt{Albums} starting with \texttt{1} are located in the same directory
(\texttt{3365}). This directory has a common prefix, i.e. \texttt{1}, from the
\texttt{Users} table. The same principle can be seen for key \texttt{2} of the
\texttt{Users} table. This interleaving of tables exploits locality relationships
of multiple tables and therefore is significant for Spanner's performance.

>>>>

\subsection{Directories}
\label{subsec:directories}

@@

\subsection{Data Model}
\label{subsec:data-model}

@@

Therefore, Spanner requires the application/user to partition databases into
one or more hierarchies of tables. Based on this hierarchical information, Spanner
builds the directories. A directory contains hierarchically ordered rows from
all tables of a hierarchy which belong to the same key of the topmost table of
the hierarchy. Figure~\ref{subfig:interleaved-tables} shows an example of this
concept. In this example, the \texttt{Users} table is the topmost table of the
hierarchy and the \texttt{Albums} table is one level below. As we can see, all
rows of \texttt{Albums} connected to user \texttt{1} are located in the same
directory (\texttt{3365}). This directory has a common prefix, i.e. \texttt{1},
from the \texttt{Users} table. The same principle can be seen for key \texttt{2}
of the \texttt{Users} table. This interleaving of tables exploits locality
relationships of multiple tables and therefore is significant for Spanner's
performance.
